Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Cleaned up SUPERCOP discussion

\subsection{Chosen implementations}

\input{tables/sha3_implementations}

@@

\section{Reliability of \ac{SUPERCOP} results}

@@

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no {\verb Update() }
function available for all implementations, and that \ac{SUPERCOP} only
measures speed of hashing full byte strings. This is also a hassle for a
programmer who wants to use the implementations in \ac{SUPERCOP}

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not conform to the \ac{KAT}s supplied.

\paragraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computers measured by
\ac{SUPERCOP}.

>>>>

\subsection{Chosen implementations}
\label{sec:chosen_implementations}
\input{tables/sha3_implementations}

@@

\section{Reliability of SUPERCOP results}

@@

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no {\verb Update() }
function available for all implementations, and that \ac{SUPERCOP} only
measures speed of hashing full byte strings. We are questioning if this
discriminates implementations which actually can do more of their processing on
a call to {\verb Update() }. This is also a hassle for a programmer who wants
to use the implementations found in \ac{SUPERCOP}

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not conform to the \ac{KAT}s supplied or
implementations which fail completely as hash functions, see section
\ref{sec:choosen_implementations} for details on the JH implementation.
